---
title: "Question 4"
output:
  bookdown::html_document2:
    css: css/analysis.css
    toc: false
    number_sections: no
    self-contained: true
    fig_caption: yes
  bookdown::pdf_document2:
    toc: false
    number_sections: no
    fig_caption: no
---

```{r setup, include = FALSE}
# knitr options
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.align = 'center',
                      fig.width = 7, fig.height = 5, cache = FALSE)

# Forces any incline R to only have 2 digits and a comma for the thounsands place
knitr::knit_hooks$set(
          size = function(before, options, envir) {
                  if (before) return(paste0("\n \\", options$size, "\n\n"))
                  else return("\n\n \\normalsize \n")
                  }
          , inline = function(x) {if(!is.numeric(x)){ x }else{ prettyNum(round(x,3), big.mark=",") } }
          )

# Create folder structure
data_path <- "data"; viz_path <- "viz"
purrr::walk(c(data_path, viz_path), dir.create, showWarnings = FALSE)
```

```{r load-packages}
pacman::p_load(tidyverse, broom, modelr, GGally, olsrr, pander, stargazer)
```

```{r, include = FALSE}
regression_results <- function(title, ...) {
  stargazer(..., header=FALSE, no.space = TRUE, intercept.bottom = FALSE, 
            report=('vc*p'), title = title, omit.stat=c("f", "ser"),
            type = knitr::opts_knit$get("rmarkdown.pandoc.to"))
}

panderOptions('big.mark', ",")
```

```{r read-in-hertz-data}
hertz_data <- 
  read_csv(file.path(data_path, "cust_survey_transaction.csv")) %>%
  rename(`Total_charge_USD` = `Total _charge_USD`)
```

```{r results = 'asis'}
hertz_data %>% 
  select_if(function(x) any(is.na(x))) %>%
  summarise_all(funs(sum(is.na(.)))) %>%
  gather(Column, `Missing Values`) %>%
  pander(justify = c('left', 'right'))
```

We will not use the `Overall_Exper` column because 28,045 records have no response - 35% of the customer responses.

# A

We treat the survey questions continuous variables, though we know they are actually ordinal and discrete. 

```{r results = 'asis'}
base_formula <- as.formula(Recom_mend_Hertz ~ Staff_Courtesy +  
                             Speed_of_Service + Trans_Billing_as_Expected + 
                             Value_for_the_Money + Total_charge_USD + 
                             Veh_Equip_Condition + Survey_checkout_diff)
lm1 <- lm(base_formula, data = hertz_data)
regression_results(lm1, title = "Full Model Results")
```

We see that increases in all survey questions and an increase in `Total_charge_USD` are associated with an increase in response to recommending Hertz. We note that `Survey_checkout_diff` is significant at the 95% but not the 99% confidence. For a more parsimonious model, we remove this variable. 

## Multicolinearity

We would expect that many survey questions are correlated thus resulting in issues with multicolinearity. One measure of multicolinearity is *variance inflation factors* (VIF) - a measure of how much the variance of each regression coefficient $\beta_k$ is inflated by the existence of correlation among the predictor variables in the model^[https://cran.r-project.org/web/packages/olsrr/vignettes/regression_diagnostics.html]. There are lots of "rules-of-thumb" about what qualifies as a VIF that is indicates multicollinearity. A VIF of 4 is often indicates a need to investigate and while that's not the case here, can should still investigate further.

$$VIF = \frac{1}{1 - R^2_k}$$

```{r results = 'asis'}
ols_vif_tol(lm1) %>% pander()
```

We then look at a correlation plot of each of the variables (including `Overall_Exper`) in the model:

```{r fig.cap = "Pearson's Correlation Coefficient between each variable in model", fig.width = 7, fig.height = 4, fig.pos = 'h'}
hertz_data %>%
  select(Recom_mend_Hertz, Overall_Exper, Staff_Courtesy, Speed_of_Service, 
         Veh_Equip_Condition, Trans_Billing_as_Expected,  Value_for_the_Money, 
         Total_charge_USD, Survey_checkout_diff) %>%
  ggcorr(label = TRUE, size = 2, hjust = 0.75, layout.exp = 1)
```

We then perform step-wise backwards elimination (using $p$-values) to remove variables from the model:

```{r results = 'asis'}
lm2 <- update(lm1, . ~ . - Survey_checkout_diff)
regression_results(lm1, lm2, title = "Model Comparison")
```

## Results

Variable importance is indicated by the value of each coefficient's test statistic. So we sort the coefficient estimates on the test statistic. 

For each of the survey questions below, we can say that a one-unit increase in the variable is associated with a $\beta_k$ increase in response to the question about recommending Hertz. For example, a one-unit increase in reponse to the question on `Value_for_the_Money` is associated with a 0.29 increase in the question to about recommending Hertz.

```{r results = "asis"}
tidy(lm2) %>% 
  as_tibble() %>% 
  filter(term != "(Intercept)") %>% 
  arrange(desc(statistic)) %>%
  select(term, statistic, estimate) %>%
  pander(justify = c('left', 'right', 'right'))
```

# B

To test if the relationships change by Rental Location Type, Rental Purpose, and Booking Channel, we individual add each to the base model. The results are shown in \@ref(tab:part-b-table):

```{r part-b-table, results = 'asis'}
lm3 <- update(lm2, . ~ . + rent_loc_type)
lm4 <- update(lm2, . ~ . + Purpose_of_Rental)
lm5 <- update(lm2, . ~ . + as.factor(booking_channel_dummy))
regression_results(lm2, lm3, lm4, lm5, 
                   title = "Rental Location Type, Rental Purpose, and Booking Channel")
```

1. **Rental Location Type**: Yes - all survey question responses held constant, picking up the rental car at the airport increases the response about recommending Hertz by 0.044 points. In reality, this would not translate into a full point. 
2. **Rental Purpose**: No - all survey question responses held constant, the purpose of the rental has not impact.
3. **Booking Channel**: Yes - all survey question responses held constant, booking through hertz.com increases the response about recommending Hertz by 0.104 points. In reality, this would not translate into a full point. 

# C

Useful features to segment customers on need to meet the following criteria:

1. intrinsic to the customer or the customer's experience with Hertz
2. contain variation (i.e `rent_corp_lic` is split 95% and 5%)
3. not contain too many levels (i.e. segmenting on all US/CN states would not be helpful)

We will explore a few in this dataset:

## Customer Tier

```{r results = 'asis'}
hertz_data %>%
  group_by(cust_tier_code) %>%
  summarise(n = n(), mean = mean(Recom_mend_Hertz, na.rm = TRUE)) %>%
  arrange(desc(n)) %>%
  pander()
```

```{r results = 'asis'}
lm6 <- update(lm2, . ~ . + cust_tier_code)
anova(lm6, lm(lm2$call, data = lm6$model)) %>%
  pander(missing = "")
```

## Country

```{r results = 'asis'}
hertz_data %>%
  group_by(addr_country) %>%
  summarise(n = n(), mean = mean(Recom_mend_Hertz, na.rm = TRUE)) %>%
  arrange(desc(n)) %>%
  head(10) %>%
  pander()
```

```{r results = 'asis'}
lm7 <- update(lm2, . ~ . + addr_country)
anova(lm7, lm(lm2$call, data = lm7$model)) %>%
  pander(missing = "")
```

## Rental Day 

```{r result = 'asis'}
hertz_data %>%
  select(Recom_mend_Hertz,  rent_day) %>%
  group_by(rent_day) %>%
  summarise(n = n(), mean = mean(Recom_mend_Hertz, na.rm = TRUE)) %>%
  arrange(rent_day) %>%
  pander()
```

```{r result = 'asis'}
lm8 <- update(lm2, . ~ . + rent_day)
anova(lm8, lm(lm2$call, data = lm8$model)) %>%
  pander(missing = "")
```

## Difference in Car Reserved and Car Given

```{r results = 'asis'}
hertz_data %>%
  mutate(is_same = if_else(xgra_veh_class == xgra_vclass_reserv, "Same", "Different")) %>%
  group_by(is_same) %>%
  summarise(n = n(), mean = mean(Recom_mend_Hertz, na.rm = TRUE)) %>%
  pander()
```

```{r results= 'asis'}
lm9 <- lm(update(lm2$call$formula, ~. + is_same), data = hertz_data %>% 
             mutate(is_same = if_else(xgra_veh_class == xgra_vclass_reserv, "Same", "Different")))
anova(lm9, lm2) %>% 
  pander(caption = "ANOVA for model with", missing = "")
```

## D

1. The segmentation exercise only involved customers who had completed a survey. The respondents likely have a more positive view of Hertz than the typical customer. Rather than segment based on someone's response "how likely are you to recommend", Hertz could track the referrals people make to others as this represents behavior rather than perceived intent.
2. We are segmenting customers based on their responses to other survey questions. This bias does not really help make this segmentation actionable as it's merely descriptive. This analysis only helps tell us that "value for money" is driver in someone's propensity to recommend, but it does not enable future targeting. Segmentation based only on customer characteristics (i.e. age, location, income, vehicle use-case) is much more actionable. 
3. We treated an ordinal discrete variables (survey responses on a 1-9 scale) as a continuous variable. We could have performed the analysis using parametric tests that are more suitable to likert scale data.

